--- 
title: "How To: Snakemake and Git Actions in Bookdown"
subtitle: "Practical user guides with integrated solutions"
author: "Teresia Mrema-Buza, A Bioinformatics and Data Science Enthusiast"
date: "Updated on `r Sys.Date()`"
site: bookdown::bookdown_site
output:
  bookdown::bs4_book:
    template: bs4_template.html
documentclass: book
classoption: openany
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: true
always_allow_html: true
fig_caption: true
fontsize: 12pt
geometry: margin=1in
indent: false
keep_tex: true
mainfont: Times New Roman
github-repo: tmbuza/my-rmarkdown-snakemake
email_address: tmbuza@complexdatainsights.com
description: "The output format for this example is bookdown::gitbook."
---

<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Montserrat:ital@1&display=swap" rel="stylesheet">

# Getting Started with bs4 Bookdown Document

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.name/tinytex/>.

```{r include=FALSE}
knitr::write_bib(
  c(.packages(), 
    'bookdown', 
    'knitr', 
    'rmarkdown'), 'packages.bib')

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  cache = FALSE,
  comment = NA,
  fig.path='./visuals/',
  fig.show='asis',
  dev = 'png',
  fig.align='center',
  out.width = "70%",
  fig.width = 7,
  fig.asp = 0.7,
  fig.show = "asis"
)
```


```{css echo = FALSE}
/* .author, .title {
  display: none;
}

.main-container {
  max-width: 100%;
}

body {
  background-color: black;
  color: #f5f5f5;
  font-size: 1.0vw;
  font-family: "Montserrat", sans-serif;
} */
```


```{r child='01-intro.Rmd'}

```


```{r child='02-literature.Rmd'}

```


```{r child='03-method.Rmd'}

```


```{r child='04-application.Rmd'}

```


```{r child='05-summary.Rmd'}

```


```{r child='06-references.Rmd'}

```

Last updated on `r Sys.time()`  
This code was compiled by [TMB](mailto:`r rmarkdown::metadata$email_address`), it is available [here](`r rmarkdown::metadata$github_repo`).  
Reference: See the reference chapter for amazing tutorials that led to development of this practical guide.  
